%-------------------------
% Resume in Latex
% Author : Talha Hanif Butt


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Talha Hanif Butt}} & Email : \href{mailto:thanifbutt@gmail.com}{thanifbutt@gmail.com}\\
  \href{https://sites.google.com/view/talhahanifbutt}{http://www.talhahanifbutt.com}& LinkedIn : \href{https://pk.linkedin.com/in/talhahanifbutt}{talhahanifbutt}\\ 
& GitHub : \href{https://github.com/thanif}{thanif}\\



\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Computer and Emerging Sciences}{Lahore}
      {Master of Science in Data Science}{Aug 2018 -- Present}
    \resumeSubheading
      {National University of Computer and Emerging Sciences}{Islamabad}
      {Bachelor of Science in Computer Science}{Aug 2013 -- June 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Artificial Intelligence Research Lab}{UET, Lahore}
      {Summer Intern}{May 2019 - Present}
      
        
          I am working on Language Translation.
        
         \resumeSubheading
      {Computer Vision and Graphics Lab}{LUMS, Lahore}
      {MS Thesis Student}{Feb 2019 - Present}
      
        
          I am working on Cross View Image Matching.

           \resumeSubheading
      {Vision Processing Lab}{ITU, Lahore}
      {Summer Intern}{Summer 2018}
      
        
          I worked on an end-to-end model for self drivivng car.
 
           \resumeSubheading
      {Recognition, Vision and Learning Lab}{FAST NUCES, Islamabad}
      {Machine Learning Intern}{Sep 2016 - May 2018}
      
        
          Worked on the problem of Mastering Tic Tac Toe using Self play and Reinforcement Learning.\\

Worked on the problem of Autonomous driving in car simulations.\\

Worked on the problem of Textual Image deblurring.\\

Worked on the problem of Neural Steganography.\\

Worked on the problem of Image Super Resolution.\\

Worked on the problem of Nerve Segmentation.

     \resumeSubheading
      {Recognition, Vision and Learning Lab}{FAST NUCES, Islamabad}
      {Summer Intern}{Summer 2016}
      
        
          Participated in DiDi Research Algorithm Competition for predicting number of drivers required in a certain area at a certain time.
          
               \resumeSubheading
      {Dr. Majid Khan}{FAST NUCES, Islamabad}
      {Research Assistant}{Aug 2015 - Dec 2015}
      
        
          Worked on the practical implementation of data security and information hiding algorithms.

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Skin Classification}
      {Built a deep learning model that classifies skin images with samples of 8 common skin pathologies and carcinoma.
}
\resumeSubItem{Sentiment Analysis}
      {Built a model for sentiment analysis of movie reviews.}
      \resumeSubItem{Indoor Self Driving Car}
      {Built a model for driving in a corridor.}
    \resumeSubItem{Alpha Go Zero on Tic Tac Toe}
      {Mastering tic tac toe using self play and reinforcement learning.}
           \resumeSubItem{Autonomous Driving in Car Simulations}
      {Worked on simulators including Carla and TORCS along with Euro Truck Simulator 2.}
    \resumeSubItem{Nerve Segmentation}
      {Predict nerve structure from ultrasound images of the
neck.}
    \resumeSubItem{Fish Localization}
      {Predict bounding box of fishes in images.}
       \resumeSubItem{User Activity Recognition}
      {Predict user activity based on sensor's data.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, C/C++, R, C\#, Java, Go, JavaScript, MATLAB/Octave, Lua}}
      \\
      \item{
     \textbf{Frameworks}{: Tensorflow, Scipy, Keras, Scikit-learn, OpenCV, Caffe, Torch, Django}}
     \\
     \item{
     \textbf{Others}{: Bash, Git, Android, Latex, SSH}}
    
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
